### 2016-02-21 experiments.tex
edited

Over all mutants, and all pairs of test cases repaired by the same mutant (so the same pair may count many times, if many mutants repair both test cases), the probability of being due to the same fault was 42.77\%, and the probability of being due to the same fault if two test cases disagreed on a repair (the mutant repaired one test case but not the other) was only 20.33\%.  The baseline rate for same-fault for test pairs was 33.64\%.  Just knowing that two test cases have \emph{one} shared repairing mutant makes it 1.27x more likely that they are the same fault, and knowing they differ for one mutants makes it 0.6 times as likely they are due to the same fault.  As suspected, while matching non-repair provided some evidence, that evidence was quite weak:  only a 34.14\% chance of matching fault.

@@

Table \ref{gcctable} shows localization results for GCC 4.3.0 wrong code faults.  For the same reasons as with SpiderMonkey, only some faults were deemed to have a strong enough ground truth patch for localization evaluation.   MUSE performed poorly, with no useful (by the standard of having at least one faulty statement in the top 30) localizations.  {\bf Coverage} produced one very good localization, and was the only method to localize that fault at all, but this was its only useful localization.  MUSEUM provided two respectable localizations, but no very high quality localizations.  Only {\bf Repair} performed extremely well:  while it only localized three faults, those localizations were all extremely useful.

>>>>

Over all mutants, and all pairs of test cases repaired by the same mutant (so the same pair may count many times, if many mutants repair both test cases), the probability of being due to the same fault was 42.77\%, and the probability of being due to the same fault if two test cases disagreed on a repair (the mutant repaired one test case but not the other) was only 20.33\%.  The baseline rate for same-fault for test pairs was 33.64\%.  Just knowing that two test cases have \emph{one} shared repairing mutant makes it 1.27x more likely that they are the same fault, and knowing they differ for one mutants makes it 0.6 times as likely they are due to the same fault.  Matching non-repair provides very weak evidence:  only a 34.14\% chance of matching fault.

@@

Table \ref{gcctable} shows localization results for GCC 4.3.0 wrong code faults.  For the same reasons as with SpiderMonkey, only some faults were deemed to have a strong enough ground truth patch for localization evaluation.   MUSE performed poorly, with no useful (by the standard of having at least one faulty statement in the top 30) localizations.  {\bf Coverage} produced one very good localization, and was the only method to localize that fault at all, but this was its only useful localization.  MUSEUM provided three useful localizations, but no very high quality localizations.  Only {\bf Repair} performed extremely welwith useful localizations for 5 faults, and localizations with the fault in the top-5 statements for 4 of these.
